---
title: "Leistungsnachweis_R"
author: "Mirko Bristle"
date: "27 10 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# fortgeschrittene Datenanalyse mit R

## Setup: (always run first)
```{r}
#create Operating System Path prefix
if (Sys.info()['sysname'] == "Darwin" ) {
  SysDir="/Volumes/SNFAue/"} else {
    SysDir = "N:/"}
# load necessary library files
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(readr)
p_load(lme4)
p_load(tableone)
p_load(tidyverse)
p_load(ggplot2)
p_load(merTools)
p_load(brms)
p_load(shinystan)
p_load(ggeffects)


```

## Einlesen der Daten:

todo: biopac subject 2 ist komisch.

```{r}
options(max.print = 99999999)
PhysioData_org<-read_rds(paste0(SysDir,"SoOp/deprecated/Soccer deprecated/original/analysis/ECG/AggregatedData/PhysioData_org_noArt_3sdMarked_.rds"))

#exclude Bsp trails
PhysioData<-PhysioData_org  %>% filter(!grepl("Bsp",Spielfeld))
#create condition
PhysioData$Factor1<-if_else(grepl(paste(c("Selbst","Ingroup1","Ingroup2"),collapse="|"),PhysioData$Gruppe),"Us","Them")
PhysioData$Factor2<-if_else(grepl(paste(c("Selbst","Konkurrent"),collapse="|"),PhysioData$Gruppe),"Single",
                             if_else(grepl(paste(c("Ingroup1","Outgroup1"),collapse="|"),PhysioData$Gruppe),"Team_1","Team_2")) 
#make Participant ID unique by adding the between group to the name
PhysioData$BiopacSubject<-paste0(if_else(PhysioData$betweenCond=="soccerPlayer","sp","nsp"),"_",PhysioData$BiopacSubject) %>% as.character()
#PhysioData$BiopacSubject<-if_else(PhysioData$BiopacSubject=="sp_10","sp_9",PhysioData$BiopacSubject) #error in recording
PhysioData<-PhysioData %>% filter(BiopacSubject!="sp_9")
PhysioData<-PhysioData %>% filter(BiopacSubject!="sp_10")
#aggregate spielfeld 
PhysioData$Spielfeld<-as.numeric(as.character(unlist(PhysioData$Spielfeld)))%%16+1
#drop biopactrail (only from merging)

col <- c("Target","Measurement", "BiopacSubject","BiopacTrail","Time","Gruppe","betweenCond","Spielfeld","Factor1","Factor2")
PhysioData["Time"]<-as.numeric(as.character(unlist((PhysioData["Time"]))))
PhysioData[col]<-lapply(PhysioData[col],factor)
sapply(PhysioData, class)

if(F){  
tbo<-CreateTableOne(data = PhysioData )
summary(tbo) 
}
rm(col,PhysioData_org)
```

## Plots Measurement by Subject

Phight:
- nsp_14: grosse varianz nach oben - exclude
- nsp_17/20 bottem effekt - 0
- nsp_7: alles null

PRQ:
nicht interpretierbare Verteilungen

QT:
- nsp_14 riesige varianz exclude
- nsp_7 alles null

QTwidth:
sehr komische Verteilungen, viele nullen, bei 100 beschränkt ?? komisch

Rhight:
- nsp_3 viele 0 
- nsp_7 alles 0
- nsp_14 riesige varianz exclude
- nsp_4 grosse varianz

RRi:
- nsp_3 lot of values at 0 --> exclude
- nsp_14 grosse varianz

ST: 
- nsp_7 alles 0
- ausreisser bei nsp_16, nsp_4 und sp_14 (Werte zwischen 10 und 70) -> filtern
- nsp4,5,6 grosse varianz

STev:
- prakisch alle nsp haben bottem effekt
- nsp_4 grosse varianz
- nsp_14 riesen varianz exclude


--> nur analyse von Phight, QT, Rhight, RRi, ST

```{r}
plotMeasurementBySubject<- function(measurement,string){
    measurement<-measurement %>% filter(Measurement==string)
    ggplot(data = drop_na(measurement),mapping = aes(x = BiopacSubject, 
                         y = Value, 
                         fill = Measurement)) +
                      geom_violin() +
                      geom_jitter(width = 0.2, alpha = 0.6) +
                      theme_classic()
}
#Phight:
PhysioData %>% filter(BiopacSubject!="nsp_14")  %>%  plotMeasurementBySubject("Phight")
#PRQ
PhysioData  %>% filter(BiopacSubject!="nsp_14") %>%  plotMeasurementBySubject("STev")
#QT
PhysioData %>% filter(BiopacSubject!="nsp_14") %>% plotMeasurementBySubject("QT")
#QTwidth
PhysioData %>% filter(BiopacSubject!="nsp_14") %>%  plotMeasurementBySubject("QTwidth")
#RRi
PhysioData %>% filter(BiopacSubject!="nsp_14") %>%  plotMeasurementBySubject("RRi")
#Rhight
PhysioData %>% filter(BiopacSubject!="nsp_14") %>%  plotMeasurementBySubject("Rhight")
#ST
PhysioData %>% filter(BiopacSubject!="nsp_14") %>% filter(Value<=3) %>%  plotMeasurementBySubject("ST")
#STev
PhysioData  %>% filter(BiopacSubject!="nsp_14") %>% plotMeasurementBySubject("STev")

#exclude:

PhysioData_1 <- PhysioData %>% 
  filter(BiopacSubject!="nsp_14") %>% 
  filter(BiopacSubject!="nsp_3") %>% 
  filter(BiopacSubject!="nsp_7") %>% 
  filter(!(Measurement=="ST" & Value>=3)) %>% 
  filter(  Measurement=="Phight" 
         | Measurement == "QT" 
         | Measurement == "Rhight" 
         | Measurement == "RRi"
         | Measurement == "ST") 
PhysioData_1$VasSlide.RT<-if_else(PhysioData_1$VasSlide.RT!=0,PhysioData_1$VasSlide.RT,NULL)


```

#TimePlot
```{r}
 physio_RRi<-na.omit(filter(PhysioData_1,(Measurement=="RRi")&(grepl("Stimulus",Target))&(Time!=-2)))

# Separate regressions of mpg on weight for each number of cylinders
qplot( Time, Value, data= physio_RRi, geom=c("point", "smooth"), 
   method="lm", formula=y~x, color=BiopacSubject, 
   main="Regression of BPM on Time", 
   xlab="Time", ylab="BPM")

qplot(Time, Value, data=physio_RRi, geom=c("boxplot"), 
   fill=Time, main="Kategorial Time (s) against BPM",
   xlab="Time(s)", ylab="BPM")


mg <- ggplot(physio_RRi, aes(x = VasSlide.RT, y =VasSlide.VAS ,colour = factor(BiopacSubject))) + geom_point()
mg + facet_grid(Factor1 + Factor2 ~ betweenCond)
```

## brms model
```{r}
options (mc.cores=parallel::detectCores ()) # Run on multiple cores

getBRMModel <- function(dataframe=NULL,form=NULL,measurement=NULL,data=NULL,name=NULL,path="",family = NULL, prior=NULL,autocor=NULL) {
    options (mc.cores=parallel::detectCores ()) # Run on multiple cores
    if (!is.null( dataframe)){
      form=formula(dataframe$formulas)
      name=dataframe$names
      measurement=dataframe$measurement
    }
    assertthat::not_empty(formula)
    assertthat::not_empty(data)
    assertthat::not_empty(name)
    assertthat::not_empty(measurement)
    
    tryCatch(
      {
        data<- filter(data,Measurement==measurement)
      },
        error=function(cond) {
          message(cond)
      }
    )
    
  
  
    out <- tryCatch(
        {
            read_rds(paste0(path,measurement,"_",name,".rds"))
        },
        error=function(cond) {
            message(cond)
            #cat(paste("\n\nFile does not seem to exist: ", paste0(path, name), "\nnew Model will be calculated and saved with the specified name. \nGo grab a cup of coffee  and do 10 Push-ups:)\n\n"))
            
            #model<-brm(formula,data = data,prior=prior,family = family, autocor=autocor)
            #saveRDS(model,paste0(path,measurement,"_",name,".rds"))
            #return(model)
        }
    )    
    return(out)
}

```


### Verhalten 
```{r}
p_load(readxl)
sp<-read_excel(paste0(SysDir,
                      "SoOp/deprecated/Soccer deprecated/original/rawDaten/soccerPlayer/E-Prime Daten/Merge_VP01_VP30.xlsx")) 
sp$betweenCond<-"soccerPlayer"
nsp<-read_excel(paste0(SysDir,
                       "SoOp/deprecated/Soccer deprecated/original/rawDaten/nonSoccerPlayer/E-Prime Daten/Merge_VP01_VP30.xlsx")) 
nsp$betweenCond<-"nonSoccerPlayer"
behaviorData<-rbind(sp,nsp) %>% select( c(Name,Gruppe,betweenCond,Spielfeld,VasSlide.RT,VasSlide.VAS))
behaviorData<-behaviorData %>% filter(!grepl("Bsp",Spielfeld))
#create condition
behaviorData$Factor1<-if_else(grepl(paste(c("Selbst","Ingroup1","Ingroup2"),collapse="|"),behaviorData$Gruppe),"Us","Them")
behaviorData$Factor2<-if_else(grepl(paste(c("Selbst","Konkurrent"),collapse="|"),behaviorData$Gruppe),"Single",
                             if_else(grepl(paste(c("Ingroup1","Outgroup1"),collapse="|"),behaviorData$Gruppe),"Team_1","Team_2")) 
#aggregate spielfeld 
behaviorData$Spielfeld<-as.numeric(as.character(unlist(behaviorData$Spielfeld)))%%16+1
behaviorData$VasSlide.RT<-if_else(behaviorData$VasSlide.RT!=0,behaviorData$VasSlide.RT,NULL)
#plot
mg <- ggplot(behaviorData, aes(x = VasSlide.RT, y =VasSlide.VAS ,colour = factor(Name))) + geom_point()
mg + facet_grid(Factor1 + Factor2 ~ betweenCond)
#Modeling
saveRDS(behaviorData,"behavior.rds")

# EXECUTE brms_b.R to generate Models!

models<-data_frame(list("m0",
             "m1a",
             "m1b",
             
             "m2",
             "m2a",
             "m2b",
             "m2c"
             )) 
colnames(models)[1]<-"names"
models$measurement<-"VAS"
models <- split(models, seq(nrow(models)))
M<- lapply(models,function(x){read_rds(paste0("mod/",x$measurement,"_",x$names,".rds"))})

loo_behavior<- loo(M$`1`,M$`2`,M$`3`,M$`4`,M$`5`,M$`6`,M$`7`,pointwise = F,cores = parallel::detectCores ())

dat <- ggpredict(M$`4`, terms = c("Factor1", "Factor2"),
ppd=T)
plot(dat,alpha = 0.05, dodge = 0.5)
```

### Reaction Times
```{r}
models<-data_frame(list("m0",
             "m1a",
             "m1b",
             
             "m2",
             "m2a",
             "m2b",
             "m2c"
             ))
colnames(models)[1]<-"names"
models$measurement<-"RT"
models <- split(models, seq(nrow(models)))
M_RT<- lapply(models,function(x){read_rds(paste0("mod/",x$measurement,"_",x$names,".rds"))})
loo_RT<- loo(M_RT$`1`,M_RT$`2`,M_RT$`3`,M_RT$`4`,M_RT$`5`,M_RT$`6`,M_RT$`7`,pointwise = F,cores = parallel::detectCores ())

dat <- ggpredict(M_RT$`4`, terms = c("Name"),
ppd=T)
plot(dat,alpha = 0.05, dodge = 0.5)
```



### Physiologie 
#### Phight
```{r}
library(pacman)
p_load(brms)
p_load(dplyr)
p_load(readr)
models<-data_frame(c("m0",
               
             "m1a",
             "m1b",
             #"m1c",
             
             #"m2",
             "m2a",
             
             "m2b",
             "m2c", 
             
             "m3a"#,
             #"m3b"
             ))

colnames(models)[1]<-"names"
models$measurement<-"Phight"
models <- split(models, seq(nrow(models)))
M_Phight<- lapply(models,function(x){read_rds(paste0("models/",x$measurement,"_",x$names,".rds"))})
loo_Phight<- loo(M_Phight$`1`,M_Phight$`2`,M_Phight$`3`,M_Phight$`4`,M_Phight$`5`,M_Phight$`6`,M_Phight$`7`,pointwise = F,cores = parallel::detectCores ()) #
saveRDS(loo_Phight,"models/loo_Phight.rds")

lapply(M_Phight,function(x){x$formula})

dat <- ggpredict(M_Phight$`7`, terms = c("Factor1","Factor2","betweenCond"),ppd=T)
plot(dat,alpha = 0.05, dodge = 0.5)

```

#### QT
```{r}
library(pacman)
p_load(brms)
p_load(dplyr)
p_load(readr)
models<-data_frame(list("m0",
               
             "m1a",
             "m1b",
             #"m1c",
             
             #"m2",
             "m2a",
             
             "m2b",
             "m2c", 
             
             "m3a"#,
             #"m3b"
             ))

colnames(models)[1]<-"names"
models$measurement<-"QT"
models <- split(models, seq(nrow(models)))
M_QT<- lapply(models,function(x){read_rds(paste0("models/",x$measurement,"_",x$names,".rds"))})
#loo_QT<- loo(M_QT$`1`,M_QT$`2`,M_QT$`3`,M_QT$`4`,M_QT$`5`,M_QT$`6`,M_QT$`7`,pointwise = F,cores = parallel::detectCores ()) #,M$`4`,M$`5`,M$`6`,M$`7`
#saveRDS(loo_QT,"models/loo_QT.rds")
loo_QT<-read_rds("models/loo_Rhight.rds")
dat <- ggpredict(M_QT$`6`, terms = c("Factor1", "Factor2","betweenCond"))
plot(dat,alpha = 0.05, dodge = 0.5)
```

Rhight
```{r}
library(pacman)
p_load(brms)
p_load(dplyr)
p_load(readr)
models<-data_frame(list("m0",
               
             "m1a",
             "m1b",
             #"m1c",
             
             #"m2",
             "m2a",
             
             "m2b",
             "m2c", 
             
             "m3a"#,
             #"m3b"
             ))

colnames(models)[1]<-"names"
models$measurement<-"Rhight"
models <- split(models, seq(nrow(models)))
M_Rhight<- lapply(models,function(x){read_rds(paste0("models/",x$measurement,"_",x$names,".rds"))})
#loo_Rhight<- loo(M_Rhight$`1`,M_Rhight$`2`,M_Rhight$`3`,pointwise = F,cores = parallel::detectCores ()) #,M$`4`,M$`5`,M$`6`,M$`7`
#saveRDS(loo_Rhight,"models/loo_Rhight.rds")
loo_Rh<-read_rds("models/loo_Rhight.rds")
print(M_Rhight$`6`,digits=4)
dat <- ggpredict(M_Rhight$`6`, terms = c("Factor1", "Factor2","betweenCond"))
plot(dat,alpha = 0.05, dodge = 0.5)
```


RRi
```{r}
library(pacman)
p_load(brms)
p_load(dplyr)
p_load(readr)
models<-data_frame(list("m0",
               
             "m1a",
             "m1b",
             #"m1c",
             
             #"m2",
             "m2a",
             
             "m2b",
             "m2c", 
             
             "m3a"#,
             #"m3b"
             ))

colnames(models)[1]<-"names"
models$measurement<-"RRi"
models <- split(models, seq(nrow(models)))
M_RRi<- lapply(models,function(x){read_rds(paste0("models/",x$measurement,"_",x$names,".rds"))})
loo_RRi<- loo(M_RRi$`1`,M_RRi$`2`,M_RRi$`3`,pointwise = F,cores = parallel::detectCores ()) #,M$`4`,M$`5`,M$`6`,M$`7`
saveRDS(loo_RRi,"models/loo_RRi.rds")
loo_Rh<-read_rds("models/loo_RRi.rds")
p_load(ggeffects)
print(M_RRi$`6`,digits=4)
dat <- ggpredict(M_RRi$`6`, terms = c("Factor1", "Factor2","betweenCond"))
plot(dat,alpha = 0.05, dodge = 0.5)
```

ST
```{r}
library(pacman)
p_load(brms)
p_load(dplyr)
p_load(readr)
models<-data_frame(list("m0",
               
             "m1a",
             "m1b",
             #"m1c",
             
             #"m2",
             "m2a",
             
             "m2b",
             "m2c", 
             
             "m3a"#,
             #"m3b"
             ))

colnames(models)[1]<-"names"
models$measurement<-"ST"
models <- split(models, seq(nrow(models)))
M_ST<- lapply(models,function(x){read_rds(paste0("models/",x$measurement,"_",x$names,".rds"))})
#loo_ST<- loo(M_ST$`1`,M_ST$`2`,M_ST$`3`,pointwise = F,cores = parallel::detectCores ()) #,M$`4`,M$`5`,M$`6`,M$`7`
#saveRDS(loo_ST,"models/loo_ST.rds")
loo_ST<-read_rds("models/loo_RRi.rds")
p_load(ggeffects)
print(M_ST$`6`,digits=4)
dat <- ggpredict(M_ST$`6`, terms = c("Factor1", "Factor2","betweenCond"))
plot(dat,alpha = 0.05, dodge = 0.5)
```

#### old trash
```{r}
options (mc.cores=parallel::detectCores ()) # Run on multiple cores
physio<-na.omit(filter(PhysioData_1,(grepl("Stimulus",Target))&(Time!=-2)))
 



model0 <- getBRMModel(formula = (Value~1),data=physio_RRi,name = "brm_model0")
model1 <- getBRMModel(formula(Value ~ 1 + (1 | BiopacSubject)),data=physio_RRi,name = "brm_model1")
model2 <- getBRMModel(Value~1+betweenCond*Factor1*Factor2 + (1|BiopacSubject),
                      data=physio_RRi,name = "brm_model2")
model2a <-getBRMModel(Value~1+betweenCond*Factor1*Factor2 + (1|BiopacSubject)+ (1|Spielfeld),
                      data=physio_RRi,name = "model2a")#
model3 <- getBRMModel(Value~1+betweenCond*Factor1*Factor2+ Time + (1|BiopacSubject),
                      data=physio_RRi,name = "model3")#
model3a <-getBRMModel(Value~1+betweenCond*Factor1*Factor2* Time + (1|BiopacSubject),
                      data=physio_RRi,name = "model3a")#
#model3b <-getBRMModel(Value~1+betweenCond*Factor1*Factor2+ gp(Time) + (1|BiopacSubject),
                      #data=physio_RRi,name = "model3b")#
#model3ba <-brm(Value~1+betweenCond*Factor1*Factor2+ gp(Time, by=Gruppe) + (1|BiopacSubject),
                      #data=physio_RRi)#,name = "brm_model3aa"
#model3c <- getBRMModel(Value~1+betweenCond*Factor1*Factor2 +(1|BiopacSubject), 
 #                     data=physio_RRi, autocor = cor_bsts(formula = ~Time),name = "brm_model3c")
#model3d <- getBRMModel(Value~1+betweenCond*Factor1*Factor2 +(1|BiopacSubject), 
 #                     data=physio_RRi, autocor = cor_bsts(formula = ~Time|BiopacSubject),name = "brm_model3d")
names_RT<-list("m0",
               
             "m1a",
             "m1b",
             "m1c",
             
             "m2",
             "m2a",
             
             "m2b",
             "m2c", 
             
             "m3a",
             "m3b"
             )
formulas<-list( "Value~1",
                    
                "Value~1+(1|BiopacSubject)", 
                "Value~1+(1|Spielfeld)",
                "Value~1+(1|BiopacSubject)+(1|Spielfeld)", 
                
                "Value~1+Factor1+Factor2 + (1|BiopacSubject)+ (1|Spielfeld)",
                "Value~1+Factor1*Factor2 + (1|BiopacSubject)+ (1|Spielfeld)",
           
                "Value~1+Factor1*Factor2 + betweenCond + (1|BiopacSubject)+ (1|Spielfeld)",
                "Value~1+Factor1*Factor2 * betweenCond + (1|BiopacSubject)+ (1|Spielfeld)",
                
                "Value~1+Factor1*Factor2 * betweenCond + Time + (1|BiopacSubject)+(1|Spielfeld)",
                "Value~1+Factor1*Factor2 * betweenCond * Time + (1|BiopacSubject)+ (1|Spielfeld)"
                )


measurement<-list("Phight",
                  "QT",
                  "Rhight",
                  "RRi",
                  "ST"
                  )
models<-lapply(measurement,function(x,y){within(y,measurement<-x)},y= data_frame(formulas,names)) %>% bind_rows()

est_model<-lapply(models,function(x,y){getBRMModel(dataframe = x,y)},y=physio)


looComp<-tryCatch({
  read_rds("looComp.rds")
},
  error=function(cond) {
     message(cond)
    loo<-loo(model0,model1,model2,model2a,model3,model3a,pointwise = F,cores = parallel::detectCores ())
    saveRDS(loo,"looComp.rds")
    return(loo)
  }
)


looComp
loo(model2,model2a,pointwise = F,cores = parallel::detectCores ())




model0a <- getBRMModel(formula = (Value~1+gp(Time)),data=physio_RRi,name = "brm_model0a")

m0<-lmer(Value~betweenCond+Factor1*Factor2+Time+(1|BiopacSubject),data = physio_RRi)
p_load(sjPlot)
sjp.lmer(m0, type = "fe",p.kr=F)
 
```


Discriminance Analysis

https://tgmstat.wordpress.com/2014/01/15/computing-and-visualizing-lda-in-r/
https://tgmstat.wordpress.com/2013/11/07/unsupervised-data-pre-processing-for-predictive-modeling/

https://github.com/avrilcoghlan/LittleBookofRMultivariateAnalysis/blob/master/src/multivariateanalysis.rst

https://www.r-bloggers.com/linear-discriminant-analysis-in-r-an-introduction/ 

```{r}
p_load(devtools)
install_github("Displayr/flipStandardCharts")
install_github("Displayr/flipMultivariates")
library(flipMultivariates)


lda.2 <- LDA(Gruppe ~Value+ betweenCond +Measurement+Spielfeld+BiopacSubject+VasSlide.RT+VasSlide.VAS,
 data = PhysioData_1,
 output = "Discriminant Functions",
 prior = "Observed",
 subset = PhysioData_1$Target=="Stimulus")
print(lda.2)



p_load(ggplot2)
p_load(gridExtra)
p_load(reshape2)

p1 = ggplot(PhysioData_1 %>% filter(Measurement=="Phight")) + geom_point(aes(x = Value, y = VasSlide.VAS))

temp <- melt(PhysioData_1%>% filter(Measurement=="Phight"), measured = c("Measurement", "Gruppe"))
p2 = ggplot(temp) + geom_histogram(aes(x=value)) + 
  facet_grid(. ~ variable, scales = "free_x")
grid.arrange(p1, p2)

p_load(caret)


measures<-list(filter(PhysioData_1, Measurement=="Phight"),
               filter(PhysioData_1, Measurement=="QT"),
               filter(PhysioData_1, Measurement=="Rhight"),
               filter(PhysioData_1, Measurement=="RRi"),
               filter(PhysioData_1, Measurement=="ST"))

trans.measure<-lapply(measures,preProcess,method=c("BoxCox", "center", "scale"))
predict_measure<-rbind(
  data.frame(trans = predict(trans.measure[1], filter(PhysioData_1, Measurement=="Phight"))),
  data.frame(trans = predict(trans.measure[2], filter(PhysioData_1, Measurement=="QT"))),
  data.frame(trans = predict(trans.measure[3], filter(PhysioData_1, Measurement=="Rhight"))),
  data.frame(trans = predict(trans.measure[4], filter(PhysioData_1, Measurement=="RRi"))),
  data.frame(trans = predict(trans.measure[5], filter(PhysioData_1, Measurement=="ST")))
)

trans <- preProcess(predictors, c("BoxCox", "center", "scale"))
predictors_trans <- data.frame(trans = predict(trans, predictors))

trans <- preProcess(PhysioData_1, c("conditionalX", "center", "scale"),outcome = PhysioData_1$Measurement)
predictors_trans <- data.frame(trans = predict(trans, PhysioData_1))
predictors_trans<-predict_measure
p1 = ggplot(predictors_trans) + geom_point(aes(x = trans.Value, y = trans.VasSlide.RT))
temp <- melt(predictors_trans, measured = c("trans.Value", "trans.VasSlide.RT"))
p2 = ggplot(temp) + geom_histogram(aes(x=value), data = temp) + 
  facet_grid(. ~ variable, scales = "free_x")
grid.arrange(p1, p2)


lda.2 <- LDA(trans.Measurement~trans.Value+ trans.betweenCond +trans.Gruppe +trans.Spielfeld+trans.BiopacSubject+trans.VasSlide.RT+trans.VasSlide.VAS,
 data = predict_measure,
 output = "Prediction-Accuracy Table",
 prior ="Observed",
 subset = PhysioData_1$Target=="Stimulus")
print(lda.2)
```

